---
title: "Example of WISP.data functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example of WISP.data functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author: "Alessandro Oggioni, Nicola Ghirardi"
---

## Provide the account of your station
```{r echo = TRUE, results = 'hide', warning=FALSE, eval=FALSE}
userid <- Sys.getenv("WISP_IREA_USERID")
pwd <- Sys.getenv("WISP_IREA_PSW")
```

## Get data from the WISP station server for a single or multiple dates.

In this function if the `save_csv` parameter is set to `TRUE`, the function
will save the reflectance data as a .csv file in the 'output' folder within
the working directory.

```{r echo = TRUE, results = 'hide', warning=FALSE, message=FALSE, eval=FALSE}
reflect_data <- WISP.data::wisp_get_reflectance_multi_data(
  time_from = "2024-09-11T09:00",
  time_to   = "2024-09-17T14:00",
  station   = "WISPstation012",
  userid    = userid,
  pwd       = pwd,
  save_csv  = FALSE,
  out_dir   = tempdir()
)
```

## Quality Check (QC) of the reflectance data

In this function if the `save_csv` parameter is set to `TRUE`, the function
will save the quality checked reflectance data as a .csv file in
the 'output' folder within the working directory.

User-configurable Parameters:

- **maxPeak** (numeric): maximum allowed reflectance peak threshold. Default: 0.05
- **maxPeak_blue** (numeric): maximum allowed threshold for the blue region. Default: 0.02
- **qa_threshold** (numeric): maximum threshold for the QA index. Default: 0.5
- **qwip_threshold** (numeric): minimum threshold for the QWIP index. Default: 0.2
- **calc_scatt** (logical): if `TRUE`, computes scattering parameters and band ratios
- **calc_SPM** (logical): if `TRUE`, computes SPM concentration according to Novoa et al. (2017)
- **calc_TUR** (logical): if `TRUE`, computes TUR concentration according to Novoa et al. (2017)
- **calc_TSS** (logical): if `TRUE`, computes SPM concentration according to Jiang et al. (2021)
- **calc_gons** (logical): if `TRUE`, computes CHL concentration according to Gons et al. (2002)
- **calc_gons740** (logical): if `TRUE`, computes CHL concentration according to Gons et al. (2002)
- **calc_NDCI** (logical): if `TRUE`, computes NDCI index according to Mishra et al. (2012)
- **calc_mishra** (logical): if `TRUE`, computes CHL concentration according to Mishra et al. (2012)
- **calc_dom_wave** (logical): if `TRUE`, computes dominant wavelength and Hue Angle
- **calc_OWT** (logical): if `TRUE`, computes Optical Water Type classification

```{r echo = TRUE, results = 'hide', warning=FALSE, message=FALSE, eval=FALSE}
reflect_data_qc <- WISP.data::wisp_qc_reflectance_data(
  data           = reflect_data,
  maxPeak        = 0.05,
  maxPeak_blue   = 0.02,
  qa_threshold   = 0.5,
  qwip_threshold = 0.2,
  calc_scatt     = TRUE,
  calc_SPM       = TRUE,
  calc_TUR       = TRUE,
  calc_TSS       = TRUE,
  calc_gons      = TRUE,
  calc_gons740   = TRUE,
  calc_NDCI      = TRUE,
  calc_mishra    = TRUE,
  calc_dom_wave  = TRUE,
  calc_OWT       = TRUE,
  save_csv       = FALSE,
  out_dir        = tempdir()
)

# ----
# 106 spectral signatures were removed during QC:
# 
# - 16 spectral signatures were removed thanks to QA+QWIP
# - 2 spectral signatures were removed thanks to QC1+QA+QWIP
# - 4 spectral signatures were removed thanks to QC2+QA+QWIP
# - 1 spectral signatures were removed thanks to QC3+QC4+QA+QWIP
# - 4 spectral signatures were removed thanks to QC4+QA+QWIP
# - 79 spectral signatures were removed thanks to QC6+QA+QWIP
# 
# The spectral signature of 2024-09-11 09:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 09:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 09:30:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 09:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 10:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 10:15:05 has been removed thanks to: QA QWIP
# The spectral signature of 2024-09-11 10:30:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 10:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 11:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 11:15:05 has been removed thanks to: QC2 QA QWIP
# The spectral signature of 2024-09-11 11:30:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 11:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 12:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 12:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 12:30:06 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 12:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 13:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 13:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-11 13:30:05 has been removed thanks to: QC6 QA QWIP
# ...
# The spectral signature of 2024-09-17 09:00:05 has been removed thanks to: QC3 QC4 QA QWIP
# The spectral signature of 2024-09-17 09:15:05 has been removed thanks to: QC4 QA QWIP
# The spectral signature of 2024-09-17 09:30:05 has been removed thanks to: QA QWIP
# The spectral signature of 2024-09-17 09:45:05 has been removed thanks to: QA QWIP
# The spectral signature of 2024-09-17 10:00:05 has been removed thanks to: QA QWIP
# The spectral signature of 2024-09-17 10:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 10:30:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 10:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 11:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 11:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 11:30:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 11:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 12:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 12:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 12:30:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 12:45:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 13:00:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 13:15:05 has been removed thanks to: QC6 QA QWIP
# The spectral signature of 2024-09-17 13:30:05 has been removed thanks to: QC4 QA QWIP
# The spectral signature of 2024-09-17 13:45:05 has been removed thanks to: QC6 QA QWIP
# 
# QA remove spectral signatures with low quality based on Wei et al. (2016)
# QC1 remove spectral signatures with negative values below 845 nm
# QC2 remove spectral signatures with outliers in the NIR (840 nm > 700 nm)
# QC3 remove spectral signatures with maximum peak greater than maxPeak
# QC4 remove spectral signatures with outliers in the Blue domain
# QC6 remove 'invalid' and 'None' spectral signatures according to level2.quality
# QWIP remove spectral signatures with low quality based on Dierssen et al., 2022
# ----

```

## Skyglint Removal (SR) of the reflectance data

In this function if the `save_csv` parameter is set to `TRUE`, the function
will save the reflectance data with the sunglint removed as a .csv file in
the 'output' folder within the working directory.

User-configurable Parameters:

- **calc_scatt** (logical): if `TRUE`, computes scattering parameters and band ratios
- **calc_SPM** (logical): if `TRUE`, computes SPM concentration according to Novoa et al. (2017)
- **calc_TUR** (logical): if `TRUE`, computes TUR concentration according to Novoa et al. (2017)
- **calc_TSS** (logical): if `TRUE`, computes SPM concentration according to Jiang et al. (2021)
- **calc_gons** (logical): if `TRUE`, computes CHL concentration according to Gons et al. (2002)
- **calc_gons740** (logical): if `TRUE`, computes CHL concentration according to Gons et al. (2002)
- **calc_NDCI** (logical): if `TRUE`, computes NDCI index according to Mishra et al. (2012)
- **calc_mishra** (logical): if `TRUE`, computes CHL concentration according to Mishra et al. (2012)
- **calc_dom_wave** (logical): if `TRUE`, computes dominant wavelength and Hue Angle
- **calc_OWT** (logical): if `TRUE`, computes Optical Water Type classification

```{r echo = TRUE, results = 'hide', warning=FALSE, eval=FALSE}
reflect_data_sr <- WISP.data::wisp_sr_reflectance_data(
  qc_data       = reflect_data_qc,
  calc_scatt    = TRUE,
  calc_SPM      = TRUE,
  calc_TUR      = TRUE,
  calc_TSS      = TRUE,
  calc_gons     = TRUE,
  calc_gons740  = TRUE,
  calc_NDCI     = TRUE,
  calc_mishra   = TRUE,
  calc_dom_wave = TRUE,
  calc_OWT      = TRUE,
  save_csv      = FALSE,
  out_dir       = tempdir()
)
```

## Plot the reflectance data

In this function, you can set to `TRUE` for the parameters you want to display 
in the legend for each of the three plots (raw, QC, SR).

```{r, warning=FALSE, out.width="100%", eval=FALSE}
custom_raw <- list(
  legend_TSM  = TRUE, 
  legend_Chla = TRUE, 
  legend_Kd   = TRUE, 
  legend_cpc  = TRUE
)

custom_qc <- list(
  legend_TSM            = TRUE, 
  legend_Chla           = TRUE, 
  legend_Kd             = TRUE, 
  legend_cpc            = TRUE, 
  legend_scatt          = TRUE,
  legend_ratio          = TRUE,
  legend_novoa_SPM      = TRUE,
  legend_novoa_TUR      = TRUE,
  legend_jiang_TSS      = TRUE,
  legend_gons_CHL       = TRUE,
  legend_gons740_CHL    = TRUE,
  legend_NDCI           = TRUE,
  legend_mishra_CHL     = TRUE,
  legend_hue_angle      = TRUE, 
  legend_dom_wavelength = TRUE,
  legend_OWT_class      = TRUE,
  legend_OWT_score      = TRUE,
  legend_OWT_z_dist     = TRUE
)

custom_sr <- list(
  legend_TSM            = TRUE, 
  legend_Chla           = TRUE, 
  legend_Kd             = TRUE, 
  legend_cpc            = TRUE, 
  legend_scatt          = TRUE,
  legend_ratio          = TRUE,
  legend_novoa_SPM      = TRUE,
  legend_novoa_TUR      = TRUE,
  legend_jiang_TSS      = TRUE,
  legend_gons_CHL       = TRUE,
  legend_gons740_CHL    = TRUE,
  legend_NDCI           = TRUE,
  legend_mishra_CHL     = TRUE,
  legend_hue_angle      = TRUE, 
  legend_dom_wavelength = TRUE,
  legend_OWT_class      = TRUE,
  legend_OWT_score      = TRUE,
  legend_OWT_z_dist     = TRUE
)

fig_comparison <- WISP.data::wisp_plot_comparison(
  raw_data = reflect_data, 
  qc_data  = reflect_data_qc, 
  sr_data  = reflect_data_sr,
  raw_args = custom_raw,
  qc_args  = custom_qc,
  sr_args  = custom_sr
)
fig_comparison
```

## Plot the temporal trend

In this function, you can modify the following variables:

- **params** (character vector): list of parameters to visualize
- **aggregate** (character): defines how temporal aggregation is applied:
  - **none**: displays all individual measurements (ideal for single-day analysis)
  - **daily_mean**: calculates the daily mean and adds a ribbon (standard deviation)
  - **daily_median**: calculates the daily median
- **merge_plot** (logical): if `TRUE`, parameters sharing the same unit are overlaid in a single plot

```{r, warning=FALSE, message=TRUE, out.width="100%", eval=FALSE}
fig_trend <- WISP.data::wisp_trend_plot(
  data       = reflect_data_sr,
  params     = c("TSM", "Chla", "Novoa_SPM", "Mishra_CHL"),
  aggregate  = "daily_mean",
  merge_plot = TRUE
)
fig_trend
```